Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-11-18 paper/paper.tex
WIP. Next job, recreate the chemo-only figure with the eE model
More examples in chemo manips

\subsection*{Chemoaffinity alone}

@@

The form of the retinal receptor expression (Eq.\,\ref{e:retrcpt}) is based on
empirical measurement, but the tectal ligand expression
(Eq.\,\ref{e:tecligexp}) was chosen arbitrarily. To expand the pattern in
Fig.\,\ref{f:ch}D so that it covers the entire tectum, we needed only to
adjust the tectal ligand expression, substituting the alternative exponential
expression:
%
\begin{equation} \label{e:tecligexp2}
L_i^{\text{exp}}(x,y) = 1.05 + 0.26 \exp(1.1 x)
\end{equation}

for the tectal ligand expression.

@@

%\begin{figure}
%\includegraphics[width=\linewidth]{./images/j4_eE_GJ_wt_fig.png}
%\caption{Gradient following model with axon-axon interactions.}
%\label{f:wt}
%\end{figure}

@@

\subsection*{Is chemoaffinity alone sufficient to explain the retinotectal projection?}

This section now at start of results

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_chemo_manipulations.png}
\caption{Surgical manipulations in the chemoaffinity-only model. Row A: wildtype. Row B: 90 degree
rotation. Row C: 180 degree rotation. Row D: Graft swap}
\label{f:chsurg}
\end{figure}

>>>>

\subsection*{Chemoaffinity as the sole patterning mechanism}

@@

The form of the retinal receptor expression (Eq.\,\ref{e:retrcpt}) is based on
empirical measurement, but the tectal ligand expression
(Eq.\,\ref{e:tecligexp}) was chosen arbitrarily. To expand the pattern in
Fig.\,\ref{f:ch}D so that it covers the entire tectum, we needed only to
adjust the tectal ligand expression, substituting the alternative exponential
expression:
%
\begin{equation} \label{e:tecligexp2}
L_i^{\text{exp}}(x,y) = 1.05 + 0.26 \exp(1.1 x)
\end{equation}
%
for the tectal ligand expression.

@@

% The chemo manipulations figure is made up from 4 figures generated with
% graph_layout::g
%
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot90_fig4row1.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot180_fig4row2.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecswap_fig4row3.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_mismatch_fig4row4.json
%
\begin{figure}
\includegraphics[width=0.8\linewidth]{./images/fig_chemo_manipulations.png}
\caption{Surgical manipulations in the chemoaffinity-only model. Row A: 90 degree
rotation. Row B: 180 degree rotation. Row C: Graft swap. Row D: mismatch ablation}
\label{f:chsurg}
\end{figure}

@@
